Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
new section for hermes in the case study

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), \smonkey{}
(Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the
breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per
technique (\ref{fig:stacked-technique}).  Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number indicates
the ordering that status labels are assigned. Several of these reports
have the label ``3-Fixed'', indicating that bug fixes have been
incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{}\footnote{Microsoft announced in
  December 2018 that the Edge browser will be based on Chromium and
  ChakraCore development would be
  discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
We reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
\hermes (\Fix{? confirmed}\Mar{by the color, there is some, no?}), and
\noBugsBugsReportedSMonkey in \smonkey{} (\Fix{? confirmed}).
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation bugs (of which,
\noBugsTransplantationConfirmed were confirmed and
\noBugsTransplantationFixed were fixed) whereas differential testing
revealed \noBugsDifferentialTesting bugs (of which,
\noBugsDifferentialTestingConfirmed were confirmed and
\noBugsDifferentialTestingFixed were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of fixed bugs were similar, if we consider only those confirmed
or fixed. Most bugs we found are of moderate severity.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing.  The tools we used and the data sets of tests
and bugs are publicly available online at the following link:

@@

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual process. This is why
  \chakra is not showed in Table~\ref{tab:test-suites}.}\Mar{did not
  review part in red}

@@

\section{Discussion}
\label{sec:bugs}

>>>>

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), \smonkey{}
(Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the
breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per
technique (\ref{fig:stacked-technique}).  Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number indicates
the ordering that status labels are assigned. Several of these reports
have the label ``3-Fixed'', indicating that bug fixes have been
incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{}\footnote{Microsoft announced in
  December 2018 that the Edge browser will be based on Chromium and
  ChakraCore development would be
  discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
We reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
\hermes (\noBugsBugsConfirmedHermes confirmed), and
\noBugsBugsReportedSMonkey in \smonkey{} (\noBugsBugsConfirmedSMonkey confirmed).
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation bugs (of which,
\noBugsTransplantationConfirmed were confirmed and
\noBugsTransplantationFixed were fixed) whereas differential testing
revealed \noBugsDifferentialTesting bugs (of which,
\noBugsDifferentialTestingConfirmed were confirmed and
\noBugsDifferentialTestingFixed were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of fixed bugs were similar, if we consider only those confirmed
or fixed. Most bugs we found are of moderate severity.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure called \entente for performing test transplantation and
differential testing.  Both \entente code and the data sets of tests
and bugs are publicly available online at the following link:

@@

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.}\Mar{did not
  review part in red}

@@

\section{Case Study}
\label{sec:bugs}

In this section we describe additional experiments to better understand the effectiveness of \entente in a recently introduced JavaScript engine. We also cover additional description of a sample of bug reports.

\subsection{Finding bugs in Hermes}

\hermes is a JavaScript engine introduced by Facebook in 2019. According to its website, \hermes ``is a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
Before testing \hermes with our both test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0. We observed that only 26\% of the Test262 tests were passing at the \hermes project. When taking a closer look, we noticed that this high percentage of failing test was due to the a also high number of features not yet suported by \hermes. For instance, in its most recent release, \hermes still do not offer support for features such as Proxy, Promisse, and Async. For this reason (the low coverage of Test262 tests), we also opted not to include \hermes along with the other JavaScript engines. Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the numbers of test used in the experiments.

We then ran both test transplantation and differential testing on \hermes. To do this work, we follow the same methodology described for the others JavaScript engines. When experimenting with test transplantation, we noted many errors when replaying the \smonkey testing stuite on \hermes. This happened because \smonkey has its own assertion framework, but \hermes did not interpret these assertions, resulting in failures in all test executions from this engine. These failures did not happen when the \smonkey tests were transplanted to the other engines, though. Overall, we found and repoted three bugs on \hermes using the test transplantation technique. One of them was confirmed by the \hermes maintainers. For one of the other bugs reported, the maintainer mentioned that the bug in question was regarding a feature not yet supported (a \texttt{return} statement outside the block scope). For the third one, the maintainers diverged regarding the proper implementation of one particular item of the specification (i.e., whether a numeric escape (non-octal-eight, \texttt{\textbackslash{8}}) should be allowed or not in strict mode. The issue was closed, but the maintainers opened a new one to discuss this matter. Among the discussions, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).  As for the differential testing, we found and reported one bug on \hermes using \radamsa. As of this writing, this particular bug report was not yet addressed by any \hermes maintainer.

Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced, with many non-supported official features, engine).
